Concurrent Programming in Harmony

### 2021-04-18 book/paper.tex
Latest

To fix the code without changing the data structure, we can use
hand-over-hand locking (\autoref{ch:cds}).
\autoref{fig:queuefix} shows an implementation that uses the same
data structure as \autoref{fig:queuebug} but uses hand-over-hand locking,
both for \texttt{put}() and for \texttt{get}().  It passes all tests.

>>>>

To fix the code without changing the data structure, we can use
hand-over-hand locking (\autoref{ch:cds}).
\autoref{fig:queuefix} shows an implementation
that uses hand-over-hand locking
both for \texttt{put}() and for \texttt{get}().  It passes all tests.
